Simulations log

### 2020-05-14 simulation_study/README.Rmd
update

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews. The output

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
knitr::opts_chunk$set(echo = FALSE)
```

@@

@@

### Version information
Personal device: macos catalina 10.15.2
Cartesius supercomputer 
asreview simulation branch reorganization.

>>>>

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
```

@@

For every model, first the hyperparameters were optimized. The scripts and results for that can be found in the `hpoptimization` directory. The `simulation` directory contains scripts for simulating an automated systematic review, using the hyperparameters obtained in the optimization.

@@

### 2020-05-14 simulation_study/hpoptimization/README.Rmd
update

>>>>

The __one__ hyperparameters are used in the simulations of the current thesis. The remaining sets of hyperparameters will be used in a future project. The `config` folder contains stores all sets of hyperparameters.

## Content
The `scripts` folder contains all scripts run on the Cartesius supercomputer. The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).

The `trials` folder transforms the hyperparameter output

The `config` folder contains all sets of optimal hyperparameters.

The current readme file preprocesses the optimal hyperparameters into an `.RDS` file for a visual inspection of the hyperparameters given below.

If you have no access to Cartesius you can run optimization trials on your own device by running the following type of commands:

```{bash, eval = FALSE}

### 2020-05-14 simulation_study/simulation/README.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

createLines <- function(cond, d, hp, seed = FALSE){
  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
  files <- data.frame(c = condition, 
                    f = c("nb_max_double_tfidf",
                    "rf_max_double_tfidf",
                    "svm_max_double_tfidf",
                    "logistic_max_double_tfidf",
                    "nn-2-layer_max_double_tfidf",
                    "nb_max_double_doc2vec",
                    "rf_max_double_doc2vec",
                    "svm_max_double_doc2vec",
                    "logistic_max_double_doc2vec",
                    "nn-2-layer_max_double_doc2vec"))

  # create condition grid
  cons <- expand.grid(d = d, hp = hp, c = cond, stringsAsFactors = FALSE)
  cons <- left_join(cons, files)

  # write 
  script <- sprintf(comm, 
        # input data
        cons$d, 
        # config file details
        cons$hp, cons$c, cons$f, cons$d,
        # output file details
        cons$hp, cons$c, cons$d)

  if(seed){
    script <- paste0(script, " --init_seed 42")
  }
return(script)
}
transfer <- function(hp, c, seed = FALSE){
    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)

    if(seed){
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s_seed/%s"
    } else {
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"
    }
    result <- sprintf(txt, hp, c, hp, c)
    return(result)
}

@@

```{r, include=FALSE}
sims <- readRDS("../R/01_hyperparameter_sets.RDS")
d <- colnames(sims)
condition <- rownames(sims)
classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
names(classifier) <- c("B", "R", "S", "L", "N")
```

# create config files 
#### 01.04.2020
```{bash, eval = FALSE}
# get config files from surfsara to hard drive 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
```

Manually update config files to simulation 
Push finished ones to GH repository
Fetch github repo on surfsara

ASReview version 0.8.1

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 1 # simulation configs are up
```

# Run simulations

## hp = one

#### BCTD
```{r}
bctd <- createLines(condition[1], d=d, hp = "one")
write.table(bctd, file = "scripts/one/bctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(bctd) <- c("7883184", "7883202", "7883207", "7883209", "7883213", "7883214")
```

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c(rep("0", 6), "7949940", "7949952", "7949953", "7949954", "7949956", "7949959")
```

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 2 # simulations are running 
```

# transfer simulation files to harddrive

```{bash, eval = FALSE}
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

./cart_simulate.py simdata/wilson.csv --config_file simconfig/one/LCTD/logistic_max_double_tfidf-wilson.ini --state_file simoutput/one/LCTD/wilson/results.h5 -r 15
```

```{r}
transfer("one", condition[c(1,2,4)])
```

```{r}
# output is on harddrive
sims[condition[1], , "one"] <- 3
```

#### 02.04.2020
get config files 'all' BCTD, LCTD.

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

```{r}
# output is on harddrive
sims[condition[2], , "one"] <- 3
```

#### 03.04.2020
SCDD model

```{r}
# get config files
# manually transform
# push to github 
sims[condition[8], d, "one"] <- 1 # simulation configs are up

# run simulations 
scdd <- createLines(condition[8], d, "one")
write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
           row.names = FALSE)
 names(scdd) <- c("7950186", "7950187", "7950188", "7950189", "7950190", "7950191")
 sims[condition[8], d, "one"] <- 2 # simulations are running 
```

```{r}
 sctd <- createLines(condition[3], d, "one")
 write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(sctd) <- c("7950483", "7950484", "7950485", "7950487", "7950489", "7950490")
sims[condition[3], d, "one"] <- 2 # simulations are running
```

```{r}
rcdd <- createLines(condition[7], d, "one")
write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(rcdd) <- c("7950491", "7950493", "7950495", "7950496", "7950497", "7950499")
sims[condition[7], d, "one"] <- 2 # simulations are running
```

```{r}
lcdd <- createLines(condition[9], d, "one")
write.table(lcdd, file = "scripts/one/lcdd.txt", sep = "\t", quote = FALSE, row.names = FALSE)
names(lcdd) <- c("7965136", "7965141", "7965143", "7965145", "7965146", "7965147")
sims[condition[9], d, "one"] <- 2 # simulations are running
```

10.04.2020

```{r}
# LCTD and SCDD both failedsimulations both failed? 
# ran again 
# transfer to harddrive
transfer("one", condition[c(4,7:9)])

# sctd is not finished yet! 
sims[condition[4],,"one"] <- 3 # output is on harddrive

# sims[condition[7],,"one"] <- 3 # output is on harddrive 
# sims[condition[8],,"one"] <- 3 # output is on harddrive 
# too little space for 9, so run again

sims[condition[9],,"one"] <- 3 # output is on harddrive 
# but ace wasn't finished yet! 
```

Repeat all failed simulations

```{r}
# run again 
# transfer to harddrive 
transfer("one", condition[8])
```

15.04.2020 
```{r}
transfer("one", condition[3]) # SCTD 
sims[condition[8], , "one"] <- 3 # output is on harddrive

# BCTD run ace dataset again 
createLines(condition[1], "ace", "one") # 8018165
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/BCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/BCTD
sims[condition[1], "ace", "one"] <- 3 # output is on harddrive

# RCDD needs to go all over again
names(rcdd) <- c("8018262", "8018263", "8018264", "8018265", "8018267", "8018268")
transfer("one", "RCDD")

# SCDD need ace ptsd software virus again
# ace 8019246
# ptsd 8019247
# software 8019250
# virus 8019251
transfer("one", "SCDD")

# LCDD only ace 
createLines(condition[9], "ace", "one") # 8019423
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCDD/ace /Volumes/Gerbrich/asreview/simoutput/one/LCDD

# LCTD
# software 
createLines("LCTD", "software", "one") # 8020733
# scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCTD/software /Volumes/Gerbrich/asreview/simoutput/one/LCTD

# SCTD 
# ace ptsd software
sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
names(sctd) <- c("8025808", "8025809", "8025810")
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
createLines("SCTD", "ptsd", "one") # 8066095
createLines("SCTD", "software", "one")
```

---

23.04.2020
Simulations for ace dataset again but now with seed. 
```{r, message = FALSE}
seed_ace <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ace", "one", seed = TRUE) %>%
  noquote()
names(seed_ace) <- c(".", "8119459", "8119460", "8119461", "8119462", "8119463", "8119464")

seed_nudging <- createLines(condition[c(1, 2, 3,4,7,8,9)], "nudging", "one", seed = TRUE) %>%
  noquote()
names(seed_nudging) <- c("8119472", "8119472", "8121720", "8121721", "8121722", "8121723", "8121725")

# transfer sctd's later!(3)
noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD

```{r template, eval = FALSE}
# get config files
# manually transform
# push to github 
sims[condition[1], d, "one"] <- 1 # simulation configs are up
# run simulations 
createLines()
sims[condition[1], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[1], , "one"] <- 3 # output is on harddrive
```

>>>>

This directory contains all scripts used to simulate systematic reviews. 
Note that the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub. Instead, those files are published on the Open Science Framework, divided over 2 ..

- `scripts` -  contains all scripts run on the Cartesius supercomputer. The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
- `config` - contains the hyperparameters for every model-dataset combination. These files are called upon in the simulation command.

If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging run the following in your bash terminal:

```{bash, eval = FALSE}

@@

The simulation will output one or more `.h5` files (depending on the number of trials you choose). Please refer to the `results` folder in the root directory of this repository for a demonstration of how to analyze the resulting files.
